### 2015-06-01 alubp.tex
small edits, mostly typography + some comments

@@

(\hg J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb \forall i=1,\ldots,n,

@@

V_{n+1}&=\hg V_n,\mb\forall n\geq 0.

@@

Follows in a similar manner as the proof of Lemma~\ref{relation1}. To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\hj(i)\geq\Phi r_i(i)\geq V_0(i), \mb \forall i=1,\ldots,n$. Also from the monotone property of $T$ we have 

@@

Since $V_1=\hg V_0$, from the definition of $\hg$ in \eqref{gamdef} and the construction of $V_0$, we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb\forall n\geq 0$. So it follows that $\hj\geq V_0\geq V_1\ldots\geq \hv$.

@@

Let $\hv$ be the fixed point of the iterative scheme in \eqref{apvi} and let $\bj$ be the best possible approximation of $J^*$ as in Definition~\ref{bestproj}, then

@@

>>>>

%!TEX root =  autocontgrlp.tex

@@

(\hg J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb i=1,\ldots,n,

@@

V_{n+1}&=\hg V_n,\mb n\geq 0.

@@

Follows in a similar manner as the proof of Lemma~\ref{relation1}. To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\hj(i)\geq\Phi r_i(i)\geq V_0(i)$, $i=1,\ldots,n$. Also from the monotone property of $T$ we have 

@@

Since $V_1=\hg V_0$, from the definition of $\hg$ in \eqref{gamdef} and the construction of $V_0$, we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb n\geq 0$. So it follows that $\hj\geq V_0\geq V_1\ldots\geq \hv$.

@@

Let $\hv$ be the fixed point of the iterative scheme in \eqref{apvi} and let $\bj$ be the best possible LUB approximation of $J^*$ as in Definition~\ref{bestproj}. Then,

@@

\todoc{Can the proof be simplified similarly to that of Theorem~\ref{fxpres}? Not a high priority.}

### 2015-06-01 cartoon.tex
small edits, mostly typography + some comments

\begin{figure}[h!]
\centering
%\resizebox{columnwidth}{2cm}{
\begin{tikzpicture}[domain=-10:7.7,scale=0.6,font=\small,axis/.style={very thick, ->, >=stealth'}]
%\draw[line,thick,->] (-1,-0.625)--(4,-0.625);
%\draw[line,thick,->] (0,-1)--(0,4);
%\draw[line,thick,-](-0.2,-0.6)--(1,3);
\draw[line,thick,-](0.5,3.5)--(1,1);
\draw[line,thick,-](1,1)--(3,1.5);
\draw[line,thick,-](3,1.5)--(4,2.1);
\node[](one) at (2,2.3){\text{$J\geq TJ$}};
\node[rotate=-45](seven) at (-0.5,2.3){\text{\tiny $W^\top J\geq W^\top TJ$}};
\node[](two) at (-0.3,-0.5){\text{$\Phi r$}};
\node[](three) at (0.7,0.7){\text{$J^*$}};
%\draw[line,thick,-](0,0)--(4,2.5);
 \draw [ultra thick, draw=white, fill=gray, opacity=0.5]
       (0.5,3.5)--(1,1)--(3,1.5)--(4,2.1) -- cycle;
\draw[line,thick,-](-1,-0.625)--(3,1.8750);
 \fill (1,1)  circle[radius=2pt];
 \fill (2,1.25)  circle[radius=2pt];
 \fill (0.5,0.3125)  circle[radius=2pt];
\draw[line,dashed,-](-1,0.1)--(6,1);
\draw[line,dashed,-](-1,0.1)--(-2,5);
 \draw [ultra thick, draw=white, fill=gray, opacity=0.2]
       (-1,0.1)--(6,1)--(-2,5) -- cycle;
\node[] (four) at (2,0.8){\text{$\tilde{J}_c$}};
\node[] (six) at (0.5,-0.1){\text{$\hat{J}_c$}};
\end{tikzpicture}
%}
\caption{The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints. The main contribution of the paper is to bound $||J^*-\hat{J}_c||$.}
\label{cartoon}
\end{figure}

>>>>

%!TEX root =  autocontgrlp.tex
\begin{figure}[h!]
\centering
%\resizebox{columnwidth}{2cm}{
%\begin{tikzpicture}[domain=-10:7.7,scale=0.6,font=\small,axis/.style={very thick, ->, >=stealth'}]
\begin{tikzpicture}[domain=-10:7.7,scale=1.2,font=\normalsize,axis/.style={very thick, ->, >=stealth'}]
%\draw[line,thick,->] (-1,-0.625)--(4,-0.625);
%\draw[line,thick,->] (0,-1)--(0,4);
%\draw[line,thick,-](-0.2,-0.6)--(1,3);
\draw[line,thick,-](0.5,3.5)--(1,1);
\draw[line,thick,-](1,1)--(3,1.5);
\draw[line,thick,-](3,1.5)--(4,2.1);
\node[](one) at (2,2.3){\text{$J\geq TJ$}};
\node[rotate=-45](seven) at (-0.5,2.3){\text{\tiny $W^\top J\geq W^\top TJ$}};
\node[](two) at (-0.3,-0.5){\text{$\Phi r$}};
\node[](three) at (0.7,0.7){\text{$J^*$}};
%\draw[line,thick,-](0,0)--(4,2.5);
 \draw [ultra thick, draw=white, fill=gray, opacity=0.5]
       (0.5,3.5)--(1,1)--(3,1.5)--(4,2.1) -- cycle;
\draw[line,thick,-](-1,-0.625)--(3,1.8750);
 \fill (1,1)  circle[radius=2pt];
 \fill (2,1.25)  circle[radius=2pt];
 \fill (0.5,0.3125)  circle[radius=2pt];
\draw[line,dashed,-](-1,0.1)--(6,1);
\draw[line,dashed,-](-1,0.1)--(-2,5);
 \draw [ultra thick, draw=white, fill=gray, opacity=0.2]
       (-1,0.1)--(6,1)--(-2,5) -- cycle;
\node[] (four) at (2,0.8){\text{$\tilde{J}_c$}};
\node[] (six) at (0.5,-0.1){\text{$\hat{J}_c$}};
\end{tikzpicture}
%}
\caption{
%\normalsize 
The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints. The main contribution of the paper is to bound $||J^*-\hat{J}_c||$.}
\label{cartoon}
\end{figure}

### 2015-06-01 lubp.tex
small edits, mostly typography + some comments

\section{Least Upper Bound Projection}\label{sec:lubp}
The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
\begin{definition}\label{lubpop}
Given $J\in \R^n$, its least upper bound projection is denoted by $\Gamma J$ and is defined as 
\begin{align}\label{gamdef}
(\Gamma J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb \forall i=1,\ldots,n,
\end{align}
where $V(i)$ denotes the $i^{th}$ component of the vector $V\in \R^n$. Also in \eqref{gamdef}, $e_j$ is the vector with $1$ in the $j^{th}$ place and zeros elsewhere, and $r_{e_j}$ is a solution to the linear program in \eqref{lubplp} for $c=e_j$.
\begin{align}\label{lubplp}
r_c\stackrel{\Delta}{=}\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb &\Phi r\geq  TJ.
\end{align}
\end{definition}
\vspace{-10pt}
\begin{remark}
\mb\\
\vspace{-10pt}
\begin{enumerate}
\item The definition of LUB operator $\Gamma \colon \R^n \ra \R^n$ involves $n$ associated linear programs.
\item Observe that $\Gamma J\geq TJ$ (follows from the fact that if $a\geq c$ and $b\geq c$, then $\min(a,b)\geq c$, where $a, b, c \in \R$).
\item Given $\Phi$ and $J\in \R^n$, define $\F\stackrel{\Delta}{=}\{\Phi r|\Phi r\geq TJ\}$. Thus $\F$ is the set of all vectors in the span of $\Phi$ that upper bound $TJ$. By fixing $c$ in the linear program in \eqref{lubplp} we select a unique vector $\Phi r_c \in \F$. The LUB projection operator $\Gamma$ picks $n$ vectors $\Phi r_{e_i},i=1,\ldots,n$ from the set $\F$ and $\Gamma J$ is obtained by computing their component-wise minimum.
\item Even though $\Gamma J$ does not belong to the span of $\Phi$, $\Gamma J$ collates the various best upper bounds that can be obtained via the linear program in \eqref{lubplp}.
\item The LUB operator $\Gamma$ in \eqref{gamdef} bears close similarity to the ALP in \eqref{alp}.
\end{enumerate}
\end{remark}
\begin{definition}\label{bestproj}
The LUB projection of $J^*$ is denoted by $\bj=\Gamma J^*$.
\end{definition}
We now characterize the LUB projection operator $\Gamma$ in the following lemmas (all the proofs are presented in the Appendix). As mentioned earlier, the error analysis depends on two $\max$-norm contraction operators the first of which is $\Gamma$. The important result of this section is Theorem~\ref{fxpres} and it relates the fixed point $\tilde{V}$ of $\Gamma$ to $J^*$.
\begin{lemma}\label{bestbnd}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_\infty$, then 
\begin{align}
||J^*-\bj||_\infty\leq 2||J^*-\Phi r^*||_\infty.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef} and the construction of $V_0$, Assumption~\ref{one}, and the fact that $\Phi r^*+||J^*-\Phi r^*||_\infty \one\geq TJ^*$. To see this, note that
\begin{align}
&\Gamma J^*=\hj \geq J^*,\nn\\
&\Phi r^* +||J^*-\Phi r^*||_\infty\geq TJ^*= J^*.\nn\\
&\text{Thus,}\nn\\
&\Phi r^* +||J^*-\Phi r^*||_\infty\geq \Gamma J^*\geq TJ^*.
\end{align}
\end{proof}

\begin{lemma}\label{gmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\geq J_2$, we have $\Gamma J_1\geq \Gamma J_2$.
\end{lemma}
\begin{proof}
Choose any $i\in \{1,\ldots,n\}$ and let $r^1_{e_i}$ and $r^2_{e_i}$ be solutions to the linear program in \eqref{lubplp} for $c=e_i$ with $J=J_1$ and $J=J_2$ respectively. Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$ and $e_i^\top \Phi r^1_{e_i} \geq e_i^\top \Phi r^2_{e_i}$, i.e., $(\Phi r^1_{e_i})(i)\geq (\Phi r^2_{e_i})(i)$. The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i})(i),\mb\forall J\in \R^n$, and our choice of $i$ was arbitrary.
\end{proof}
\begin{lemma}\label{lpsol}
Let $A\in \R^{u\times v}$, $b,c\in R^u$, $x_0 \in R^v$ and $b_0=Ax_0$. Then
\begin{align}
\min\{c^\top Ax:Ax\geq b+b_0\} =\min\{c^\top Ax:Ax\geq b\}+c^\top b_0.
\end{align}
\end{lemma}
\begin{proof}
The claim can be shown by a simple change of variables.
\end{proof}
\begin{lemma}\label{gshift}
Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+k\one$, then $\Gamma J_2=\Gamma J_1+\alpha t\one$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear programs associated with $\Gamma J_1$ and $\Gamma J_2$. The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ and $x_0=\alpha t e_i$.
\end{proof}
\begin{theorem}\label{gmaxcontra}
The operator $\Gamma  \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n,$ let $\epsilon=||J_1-J_2||_\infty$. Thus,
\begin{align}\label{ineq}
J_2-\epsilon\one\leq J_1\leq J_2+\epsilon \one.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshift}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\alpha \epsilon\one\leq \Gamma J_1\leq \Gamma J_2+\alpha \epsilon\one.
\end{align}
\end{proof}
\begin{corollary}
The iterative scheme in \eqref{pvi} based on the LUB projection operator $\Gamma$ in \eqref{gamdef} converges to a unique fixed point $\tv$.
\begin{align}\label{pvi}
V_{n+1}&=\Gamma V_n,\mb \forall n\geq 0.
\end{align}
\end{corollary}
\begin{lemma}\label{gfp}
 $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, obeys $\tv\geq T\tv$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear program associated with $\Gamma \tv$. We know that $\Phi r_{e_i}\geq T \tv,\mb \forall i=1,\ldots, n$. The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_{e_j})(i)$.
\end{proof}
\begin{lemma}\label{relation1}
 $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey the relation $\tj\geq\tv\geq J^*$.
\end{lemma}
\begin{proof}
Since $\tv\geq T\tv$ it follows that $\tv\geq J^*$. Let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{pvi} with $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\tj(i)\geq\Phi r_i(i)\geq V_0(i),\mb \forall i=1,\ldots,n$. Also from the monotone property of $T$, we have 
\begin{align}\label{lineq}
\Phi r_i&\geq V_0,\nn\\
T\Phi r_i&\geq T V_0,\mbox{we also have}\nn\\
\Phi r_i\geq T\Phi r_i&\geq T V_0,\mb\text{by taking component-wise minimum},\nn\\
V_0&\geq T V_0.
\end{align}
From the first three inequalitites in \eqref{lineq}, $\Phi r_i\geq T \Phi r_i\geq T V_0, \mb\forall i=1\to n$ and hence $V_0\geq TV_0$. Since $V_1=\Gamma V_0$, from the definition of $\Gamma$ in \eqref{gamdef} we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb\forall n\geq 0$. So it follows that $\tj\geq V_0\geq V_1\ldots\geq \tv$.
\end{proof}
\input{perfbnds}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Least Upper Bound Projection}\label{sec:lubp}
The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
\begin{definition}\label{lubpop}
Given $J\in \R^n$, its least upper bound projection is denoted by $\Gamma J$ and is defined as 
\begin{align}\label{gamdef}
(\Gamma J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i),\quad i=1,\ldots,n,
\end{align}
where $V(i)$ denotes the $i^{th}$ component of the vector $V\in \R^n$. Also in \eqref{gamdef}, $e_j$ is the vector with $1$ in the $j^{th}$ place and zeros elsewhere, and $r_{e_j}$ is a solution to the linear program in \eqref{lubplp} for $c=e_j$:
\begin{align}\label{lubplp}
 r_c   \stackrel{\Delta}{=}& \argmin_{r\in \chi} c^\top \Phi r,\nn\\
 \text{s.t}& \mb \Phi r\geq  TJ.
\end{align}
\end{definition}
Note that $r_{e_j}$ depends on $J$, but this dependence is suppressed to reduce clutter. 
\vspace{-10pt}
\begin{remark}
\mb\\
\vspace{-10pt}
\begin{enumerate}
\item The definition of LUB operator $\Gamma \colon \R^n \ra \R^n$ involves $n$ associated linear programs.
\item Observe that $\Gamma J\geq TJ$ (follows from the fact that if $a\geq c$ and $b\geq c$, then $\min(a,b)\geq c$, where $a, b, c \in \R$).
\item Given $\Phi$ and $J\in \R^n$, define $\F\stackrel{\Delta}{=}\{\Phi r|\Phi r\geq TJ\}$. Thus $\F$ is the set of all vectors in the span of $\Phi$ that upper bound $TJ$. By fixing $c$ in the linear program in \eqref{lubplp} we select a unique vector $\Phi r_c \in \F$. The LUB projection operator $\Gamma$ picks $n$ vectors $\Phi r_{e_i},i=1,\ldots,n$ from the set $\F$ and $\Gamma J$ is obtained by computing their component-wise minimum.
\item Even though $\Gamma J$ does not belong to the span of $\Phi$, $\Gamma J$ collates the various best upper bounds that can be obtained via the linear program in \eqref{lubplp}.
\item The LUB operator $\Gamma$ in \eqref{gamdef} bears close similarity to the ALP in \eqref{alp}.
In fact, it is not hard to observe that $(\Gamma J)(i) = (\Phi r_{e_i})(i)$ for any $1\le i \le n$; the reason $\Gamma$ is defined the way it is so that this resembles to \eqref{alp} will be clear. \todoc{In fact, I would prefer the simpler definition without the $\min$ and then changing this remark.}
\end{enumerate}
\end{remark}
\begin{definition}\label{bestproj}
The LUB projection of $J^*$ is denoted by $\bj=\Gamma J^*$.
\end{definition}
We now characterize the LUB projection operator $\Gamma$ in the following lemmas. 
As mentioned earlier, the error analysis depends on two $\max$-norm contraction operators the first of which is $\Gamma$. The important result of this section is Theorem~\ref{fxpres} and it relates the fixed point $\tilde{V}$ of $\Gamma$ to $J^*$.
\todoc{Poor choice of symbols: $\tilde{V}$ is the fixed point of $\Gamma$ and $\hat{V}$ will be the fixed point of $\tilde{\Gamma}$? Hmm.. Not a high priority to change it, but still..}
\begin{lemma}\label{bestbnd}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_\infty$, then 
\begin{align}
||J^*-\bj||_\infty\leq 2||J^*-\Phi r^*||_\infty.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef} and the construction of $V_0$, Assumption~\ref{one}, and the fact that $\Phi r^*+||J^*-\Phi r^*||_\infty \one\geq TJ^*$. To see this, note that
\begin{align}
\Gamma J^*=\hj \geq J^*,\nn \text{ and }
\Phi r^* +||J^*-\Phi r^*||_\infty\geq TJ^*= J^*.\nn
\end{align}
Thus,
\begin{align}
\Phi r^* +||J^*-\Phi r^*||_\infty\geq \Gamma J^*\geq TJ^*.
\end{align}
\end{proof}

\begin{lemma}\label{gmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\geq J_2$, we have $\Gamma J_1\geq \Gamma J_2$.
\end{lemma}
\begin{proof}
Choose any $i\in \{1,\ldots,n\}$ and let $r^1_{e_i}$ and $r^2_{e_i}$ be solutions to the linear program in \eqref{lubplp} for $c=e_i$ with $J=J_1$ and $J=J_2$ respectively. Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$ and $e_i^\top \Phi r^1_{e_i} \geq e_i^\top \Phi r^2_{e_i}$, i.e., $(\Phi r^1_{e_i})(i)\geq (\Phi r^2_{e_i})(i)$. The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i})(i)$, $J\in \R^n$, and our choice of $i$ was arbitrary.
\end{proof}
\begin{lemma}\label{lpsol}
Let $A\in \R^{u\times v}$, $b,c\in R^u$, $x_0 \in R^v$ and $b_0=Ax_0$. Then
\begin{align}
\min\{c^\top Ax:Ax\geq b+b_0\} =\min\{c^\top Ax:Ax\geq b\}+c^\top b_0.
\end{align}
\end{lemma}
\begin{proof}
The claim can be shown by a simple change of variables.
\end{proof}
\begin{lemma}\label{gshift}
Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+t\one$, then $\Gamma J_2=\Gamma J_1+\alpha t\one$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear programs associated with $\Gamma J_1$ and $\Gamma J_2$. The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ and $x_0=\alpha t e_i$.
\end{proof}
\begin{theorem}\label{gmaxcontra}
The operator $\Gamma  \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n,$ let $\epsilon=||J_1-J_2||_\infty$. Thus,
\begin{align}\label{ineq}
J_2-\epsilon\one\leq J_1\leq J_2+\epsilon \one.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshift}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\alpha \epsilon\one\leq \Gamma J_1\leq \Gamma J_2+\alpha \epsilon\one.
\end{align}
\end{proof}
\begin{corollary}
Let $V_0$ be arbitrary and $(V_n)$ be defined recursively by
\begin{align}\label{pvi}
V_{n+1}&=\Gamma V_n, \quad n\geq 0\,.
\end{align}
Then, $V_n$ converges to the the unique fixed point $\tv$ of $\Gamma$.
\end{corollary}
\begin{lemma}\label{gfp}
 $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, obeys $\tv\geq T\tv$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear program associated with $\Gamma \tv$. We know that $\Phi r_{e_i}\geq T \tv$, for all $i=1,\ldots, n$. The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_{e_j})(i)$.
\end{proof}
\begin{lemma}\label{relation1}
 $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey the relation $\tj\geq\tv\geq J^*$.
\end{lemma}
\begin{proof}
Since $\tv\geq T\tv$ it follows that $\tv\geq J^*$. Let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{pvi} with $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\tj(i)\geq\Phi r_i(i)\geq V_0(i)$, $i=1,\ldots,n$. Also from the monotone property of $T$, we have 
\begin{align}\label{lineq}
\Phi r_i&\geq V_0,\nn\\
T\Phi r_i&\geq T V_0,\nn
\end{align}
hence we also have,
$\Phi r_i\geq T\Phi r_i \geq T V_0$, 
and so by taking component-wise minimum,
$V_0 \geq T V_0$.

From the first three inequalities in \eqref{lineq}, $\Phi r_i\geq T \Phi r_i\geq T V_0$, $i=1,\dots, n$ and hence $V_0\geq TV_0$. Since $V_1=\Gamma V_0$, from the definition of $\Gamma$ in \eqref{gamdef} we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}$, $n\geq 0$. So it follows that $\tj\geq V_0\geq V_1\ldots\geq \tv$.
\end{proof}
\input{perfbnds}

### 2015-06-01 resdisc.tex
small edits, mostly typography + some comments

			\lambda^*(s,a)&=0, \forall a \neq u^*(s),\nn

@@

The aggregation matrix $W_a$ is defined as below: $\forall i=1,\ldots,m$,

@@

W_a(i,j)&=1, \mb\forall j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\

@@

We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$. We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$. We set $c(s)=(1-\zeta) \zeta^s, \mb\forall s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$. Also note that a better performance of $W_a$ and $W_c$ in the larger system $Q_L$ tallies with a lower value of $\et$ in the smaller system $Q_S$.

@@

\FloatBarrier
\begin{table}[H]
%\resizebox{\columnwidth}{!}{
\begin{center}
\begin{tabular}{|c|c|c|c|}\hline
Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
\end{tabular}
\end{center}
%}
\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
$.}
\label{pref}
\end{table}
Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
\subsection{Reinforcement Learning}
Reinforcement Learning (RL) algorithms are useful in scenarios where the system is available in the form of a simulator or only samples can be obtained via direct interaction. In particular, in the RL setting, the model parameters $g$ and $P$ are not known explicitly and the underlying MDP needs to be solved by using sample trajectories. In short, RL algorithms are sample trajectory based solution schemes for solving MDPs whose model information is not known. RL methods learn by filtering out the noisy sample via stochastic approximation and they also employ function approximation in order to handle MDPs with large number of states. Most RL algorithms are sample trajectory based extensions of ADP methods.\\
The RL extension of the ALP formulation has been applied to the optimal stopping problem in \cite{ALP-Bor}. Function approximation is employed to approximate the square root of the Lagrange multipliers. However, since the approximation is not linear, convergence of the resulting RL algorithm cannot be guaranteed. Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.

>>>>

			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn

@@

The aggregation matrix $W_a$ is defined as below: for all $ i=1,\ldots,m$,

@@

W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\

@@

We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$. We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$. We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.

@@

\FloatBarrier
\begin{table}[H]
%\resizebox{\columnwidth}{!}{
\begin{center}
\begin{tabular}{|c|c|c|c|}\hline
Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
\end{tabular}
\end{center}
%}
\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
$.}
\label{pref}
\end{table}
Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
\subsection{Computational Complexity}
It is known that the complexity of the linear program \cite{karmarkar} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables. In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states. Thus, the complexity of obtaining the exact solution grows at a rate which is at least quadratic in the number of states. The entries of the GRLP on the other hand are of the order of $m\times k$, \todoc{$\times d$?} where the constants $m$ and $k$ are chosen to be much smaller than the number of states. We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, while computing the exact solution took about $20$ minutes.
\todoc{Sorry for the many questions, but did you also run ALP ($k=4$) with no constraint aggregation?}
 Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the original constraints of the ALP without additional computational overhead.
\subsection{Reinforcement Learning}
Reinforcement Learning (RL) algorithms are useful in scenarios where the system is available in the form of a simulator or only samples can be obtained via direct interaction. In particular, in the RL setting, the model parameters $g$ and $P$ are not known explicitly and the underlying MDP needs to be solved by using sample trajectories. In short, RL algorithms are sample trajectory based solution schemes for solving MDPs whose model information is not known. RL methods learn by filtering out the noisy sample via stochastic approximation and they also employ function approximation in order to handle MDPs with large number of states. Most RL algorithms are sample trajectory based extensions of ADP methods.\\
The RL extension of the ALP formulation has been applied to the optimal stopping problem in \cite{ALP-Bor}. Function approximation is employed to approximate the square root of the Lagrange multipliers. However, since the approximation is not linear, convergence of the resulting RL algorithm cannot be guaranteed. Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.
